---
title: "Quantile Regression quasi stepwise model selection"
author: "Andrea Spano"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Intro

Do not forget to load libraries first

```{r}
require(quantreg)
require(rqc)
require(ggplot2)
require(gridExtra)
```


## Stackloss Example

Build model list from formula

```{r}
fm_b <- rq(stack.loss~1, data = stackloss, tau = .5, method = "fn")
mod_lst <- make_model_list (formula =  stack.loss~Air.Flow+Water.Temp+ Acid.Conc.,
                              fm_base = fm_b,
                              data = stackloss, tau = .5, method = "fn", mc.cores = 1)

                 
```

Get formulae from models

```{r}
make_formula_list(mod_lst)
```

select best model in comparison with a base model 

```{r}
fm_best <- best_model (model_list = mod_lst, fm_base = fm_b)
fm_best
```

Get the formula of a single model 

```{r}
frm(fm_best)
```


Fit all models up to three variables starting from a univariate model

```{r}
stackloss_model_list <- make_best_model_list (
  formula = stack.loss~Air.Flow+Water.Temp+ Acid.Conc.,
  formula_base = stack.loss~Air.Flow, 
  formula_null = stack.loss~1,
  data = stackloss, 
  tau = .5, method = "fn",
  mc.cores = 1)
```  

get results 

```{r}
summary_all_rqc(stackloss_model_list)
```

## state_x77 Example

Build data

```{r}
state_x77 <-  as.data.frame(state.x77)  
names(state_x77) <- c("population","income","illiteracy","life_exp","murder","hs_grad","frost","area" )
```

Make list of models. Initial data contains six variables. Base model two variables. We require a model up to four vatiables

```{r}
state_x77_model_list <- make_best_model_list (
  formula = life_exp~population+income+illiteracy+murder+hs_grad+frost+area,
  formula_base = life_exp~murder+illiteracy, 
  formula_null = life_exp~1, 
  data = state_x77, 
  n_var = 4,
  tau = .5, method = "fn",
  mc.cores = 1)
```


Results for a given number of variables


```{r}
summary_single_rqc (i = 2, rqc = state_x77_model_list)
```

Results for all variables

```{r}
summary_all_rqc (rqc = state_x77_model_list, exclude_var = c("formula_best", "formula_null"))
summary_all_rqc (rqc = state_x77_model_list, exclude_var = c("formula_best", "best_model", "formula_null"), best_only = F, digits = 4)
summary_all_rqc (rqc = state_x77_model_list, exclude_var = c("formula_best", "best_model", "formula_null"), best_only = T, digits = 4)
```


## Plot 

Fit the model with all possible variables 

```{r}
state_x77_model_list <- make_best_model_list (
  formula = life_exp~population+income+illiteracy+murder+hs_grad+frost+area,
  formula_base = life_exp~1, 
  formula_null = life_exp~1, 
  data = state_x77, 
  tau = .5, method = "fn",
  mc.cores = 1)
```



```{r}
summary <- summary_all_rqc (rqc = state_x77_model_list, best_only = TRUE, digits = 7)


p_null <- ggplot(summary ) + 
  geom_line(aes(n_model_var, ratio_rho_null) , col = "darkblue") + 
  geom_point(aes(n_model_var, ratio_rho_null), col = "darkgray", size  = 3)  +
  xlab("Number of variables in model") + ylab("Ratio Rho of NULL model") 
  

p_base <- ggplot(summary ) + 
  geom_line(aes(n_model_var, ratio_rho_base) , col = "darkgreen") + 
  geom_point(aes(n_model_var, ratio_rho_base), col = "darkorange", size  = 3) +
  xlab("Number of variables in model") + ylab("Ratio Rho of base model") 

grid.arrange(p_null, p_base, ncol = 2)
```







